---
title: "R Notebook"
output: html_notebook
---


Deliverable 1: Linear Regression to Predict MPG

Use the library() function to load the dplyr package.
```{r}
library(dplyr)
library(tidyverse)
```

Import and read in the MechaCar_mpg.csv file as a dataframe.


```{r}
MechaCar_mpg_df <- read.csv('MechaCar_mpg.csv',stringsAsFactors = F) #read in dataset
head(MechaCar_mpg_df)
```
Type the following code into the R console to look at the lm() documentation in the Help pane:
```{r}
?lm()
```
Perform linear regression using the lm() function. In the lm() function, pass in all six variables (i.e., columns), and add the dataframe you created in Step 4 as the data parameter.
```{r}

```

To create a linear regression model, our R statement would be as follows:

```{r}
lm(formula = mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = MechaCar_mpg_df) #create linear model
```

```{r}
summary(lm(formula = mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = MechaCar_mpg_df)) #generate summary statistics
```




Deliverable 2: Create Visualizations for the Trip Analysis

Download the Suspension_Coil.csv file, and place it in the active directory for your R session.


```{r}
coil_table <- read.csv('Suspension_Coil.csv',check.names = F,stringsAsFactors = F)
coil_table
```

Write an RScript that creates a total_summary dataframe using the summarize() function to get the mean, median, variance, and standard deviation of the suspension coil’s PSI column.

```{r}
total_summary <- coil_table %>% summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI), SD=sd(PSI), .groups = 'keep') #Create a total summary
```

Write an RScript that creates a lot_summary dataframe using the group_by() and the summarize() functions to group each manufacturing lot by the mean, median, variance, and standard deviation of the suspension coil’s PSI column.

```{r}
lot_summary <- coil_table %>% group_by(Manufacturing_Lot) %>% summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI), SD=sd(PSI), .groups = 'keep') #Create a total summary
```

Deliverable 3: T-Tests on Suspension Coils

Wite an RScript using the t.test() function to determine if the PSI across all manufacturing lots is statistically different from the population mean of 1,500 pounds per square inch.
```{r}
plt<- ggplot(coil_table,aes(x=(PSI)))
plt + geom_density()
```


```{r}
t.test((coil_table$PSI),mu=1500) #compare sample versus population means
```
```{r}
t.test(subset(coil_table,Manufacturing_Lot=="Lot1")$PSI,mu=1500) #compare sample versus population means
```

```{r}
t.test(subset(coil_table,Manufacturing_Lot=="Lot2")$PSI,mu=1500) #compare sample versus population means

```

```{r}
t.test(subset(coil_table,Manufacturing_Lot=="Lot3")$PSI,mu=1500) #compare sample versus population means
```


