---
title: "R Notebook"
output: html_notebook
---


Use the library() function to load the dplyr package.
```{r}
library(dplyr)
```

```{r}
?read
```


Import and read in the MechaCar_mpg.csv file as a dataframe.



```{r}
MechaCar_mpg_df <- read.csv('MechaCar_mpg.csv',stringsAsFactors = F) #read in dataset
head(MechaCar_mpg_df)
```
Type the following code into the R console to look at the lm() documentation in the Help pane:
```{r}
?lm()
```
Perform linear regression using the lm() function. In the lm() function, pass in all six variables (i.e., columns), and add the dataframe you created in Step 4 as the data parameter.
```{r}

```

To create a linear regression model, our R statement would be as follows:

```{r}
lm(formula = mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = MechaCar_mpg_df) #create linear model
```

```{r}
summary(lm(formula = mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = MechaCar_mpg_df)) #generate summary statistics
```






```{r}

```

